A pipeline to analyse time-course gene expression data

### 2020-07-14 scripts/manuscript.Rmd
update

@@

# Perform prediction on the whole set of data.
kmeans_clusters = moanin:::splines_kmeans_prediction(
    y, kmeans_clusters)
```

>>>>

**EAP:** We shouldn't use any hidden functions (i.e. that use `:::` as in `moanin:::rescale_values`). We should make it a exported function if use it in workflow.

**EAP** actually, why do we need to rescale them between 0-1 rather than just a normal call to `scale`? Would it really make a difference?

@@

# Perform prediction on the whole set of data.
kmeans_clusters = moanin::: splines_kmeans_predict(
    y, kmeans_clusters)
```
